### 2018-04-30 Paper/jaccardbaetica.tex
add change discussion

%This paper explore--- resumir en dos líneas el objeto de estudio y definir que ha sido usado para ello dispersion of culture
This paper aims to understand the production dynamics in relation to a specific area within Roman Empire. Specifically, our work pretend to detect microeconomic processes focused on a commercial product from a specific province \citep{isaksen_network_2006}. We want to detect the pattern of olive oil production that link amphora workshops and amphoric stamps used to mark them. We focus here on exploring the economic relation between stamps and amphora production centres. To do this, an Ecology approach has been used to analyse the dispersion of stamps between amphora workshops.

@@

No strong relation between stamps and spatial distance have been detected in amphora workshops. Indeed, the analysis suggests that there is not connection between stamps and the same amphora workshops, excluding certain exceptions. Consequently the majority of stamps are located in different amphora workshops and only similar stamps between closer amphora workshops were found. In any case, our results show that most similar amphoric stamps were detected in closer workshops and not in other areas. These stamps tend to share the same area of production but there is not a general relation between groups of amphora workshops and area.

The hypothesis about groups of amphora workshops sharing the same stamps seems not match with the results of analysis even though there are similar stamps in closer workshops. Rather the stamps detected in closer amphorae workshops seem not move from other farthest workshops. Additionally they could have been catalogued with different names by authors (METER PONSICH Y DRESSEL) in spite of belonging to the same place or being closer between each other. We also identify different stamps in other closer workshops. 
%los que aparecen cerca son porque están cerca o puede haber confusion entre talleres

By contrast, we have located different stamps in a same amphora workshop. Neither it seems that stamps were used to specify the quality or value of the product \citep{callender}. Probably our results could be interpreted due to several reason according to previous hypotheses. The use of these amphoric stamps could be exclusively running by the owner or families to distinguish the amphora workshop (CITAR).

(aumentar)
On the other hand, it can be interpreted somehow a batch systematic organization to prepare and distribute the commodity considering that Dressel 20 type was not marked in several cases (CITAR)

it could be somehow a batch systematic organization to prepare and distribute the commodity, considering that Dressel 20 was not marked in several cases. This method was used of counting BLA BAL

An any case,

>>>>

%This paper explore--- resumir en dos líneas el objeto de estudio y definir que ha sido usado para ello dispersion of culture
This paper aims to understand the production dynamics in relation to a specific area within Roman Empire. Specifically, our work pretend to detect microeconomic processes focused on a commercial product from a specific province \citep{isaksen_network_2006}. We want to detect the pattern of olive oil production that link amphora workshops and amphoric stamps used to mark them. We focus here on exploring the economic relation between stamps and amphora production centres. To do this, an Ecology approach has been used to analyse the dispersion of stamps between amphora workshops \citep{rubio-campillo_ecology_2018}.

@@

%crear como una introducción

In this study, we aimed to analyse whether amphoric stamps could play an important role in the organization of the workshops along rivers. For that, dissimilarity index was used to detect differences.

In our analysis, no strong relation between stamps and geographic distance were detected in amphora workshops. Indeed, the analysis suggests that there is not connection between stamps and the same amphora workshops, excluding certain exceptions. Consequently the majority of stamps are located in different amphora workshops and only similar stamps between closer amphora workshops were found. In any case, our results show that most similar stamps were detected in closer workshops and not in other areas. These stamps tend to share the same area of production but there is not a general relation between groups of amphora workshops and area.

The hypothesis about groups of amphora workshops sharing the same stamps seems do not match with the results of the analysis even though there are similar stamps in closer workshops. Rather, it seems that each workshop were organized independently with different stamps. Those stamps detected in closer workshops do not move from other farthest workshops. In other words, the stamps tend to keep in the same area and different stamps were located in a same amphora workshops. 
This could be defined by several factors. Firstly, each workshop had a different organization involved to the use of stamps and they were not used in other workshops. Secondly, stamps similarity in closer workshops could be linked to a spatial pattern. It is more probably than closer workshops tend to share more traits than farthest. While the role of river was significant for the distribution of amphorae in consumption places, river connection amongst workshops was not relevant for the distribution of stamps. Finally, the distribution of stamps could have showed some research bias. In some cases, workshops have been catalogued with different names despite belonging to the same workshops or being closer between each other. Additionally, most workshops were not widely excavated.

%los que aparecen cerca son porque están cerca o puede haber confusion entre talleres
%By contrast, we have located different stamps in a same amphora workshop.

%soltar aquí las hipótesis

Neither it seems that stamps were used to specify the quality or value of the product \citep{callender}. Probably our results could be interpreted due to several reason according to previous hypotheses. The use of these amphoric stamps could be exclusively running by the owner or families to distinguish the amphora workshop (CITAR).

(aumentar)
On the other hand, it can be interpreted somehow a batch systematic organization to prepare and distribute the commodity considering that Dressel 20 type was not marked in several cases (CITAR)
it could be somehow a batch systematic organization to prepare and distribute the commodity, considering that Dressel 20 was not marked in several cases. This method was used of counting BLA BAL

An any case, no podemos precisar a qué se tratase
